---
title: "BillBoard_SQL_Vs_R"
author: "Oyetola"
date: "29/01/2022"
output: rmarkdown_document
---


#Run the code below in R Studio to install the packages once
```{r}

install.packages(tidyverse)

install.packages(lubridate)

```


#Run the code below in R Studio to load the packages at every session
```{r}

library(tidyverse)

library(lubridate)

```


#Showing the entire billboard dataset, which is with the TIDYR package.
#Note: R is case sensitive
```{r}

View (billboard)

```



#Display all Artist on the billboard
```{r}

billboard %>% 
  distinct(artist)

```


#counting the number of times an Artist appeared on the Billboard
#you may replace "Braxton, Toni" with another artist
```{r}

 billboard %>%
  select(artist)%>%
  filter(artist == "Braxton, Toni")%>%
  count(artist)%>%
  arrange(n)
  
```



#counting the number of times more that one Artist appeared on the board
```{r}

 billboard %>%
  select(artist)%>%
  filter(artist == "Madonna" | artist == "Jay-Z"| artist == "Aguilera, Christina")%>%
  count(artist)%>%
  arrange(n)
  
```


#Displaying the Artists, their track and the year they appeared on the board
#Using "Jay-Z" and "Madonna"
#The result is grouped by a created column called "YearA"
```{r}


billboard %>%
  select(artist, track,date.entered)%>%
  mutate(YearA=(year(date.entered)))%>%
  filter(artist == "Jay-Z"| artist == "Madonna")%>%
  group_by(YearA)%>%
  arrange(desc(YearA))

```


#All except "Jay-Z" and "Madonna"
```{r}


billboard %>%
  select(artist, track,date.entered)%>%
  mutate(YearA=(year(date.entered)))%>%
  filter(artist != "Jay-Z", artist != "Madonna")%>%
  group_by(YearA)%>%
  arrange(desc(YearA))

```




